\huge Cross-language Sentiment Analysis for Social Media

### 2018-08-30 submit/paper.tex
backup

Social Media is becoming more and more popular. There are lots of text comments
on different discussion topics every day.
It would be impossible to analysise the huge amount of data generated manually.
These topics are discussed by speakers of different languages, from different
cultural backgrounds, further complicating any analysis.
Most people enounter language and culture barriers during cross-language
communication.
In this paper, the use of machine translation and sentiment analysis tools to
solve this problem of analysing cross-cultural and cross-language data is
explored and discussed.
Sentiment analysis is a part of text data mining. The aim of sentiment analysis
is to determine the attitude of speakers or writers with respect to some topic
or the overall contextual polarity or emotional reaction to a text document. It is usually equated with
opinion mining, which involves the use of natural language processing and
machine learning to ascertain the possibility of positive or negative opinions \cite{sentimentAnalysis}.
Sentiment analysis is useful for analyzing a huge amount of data relating to personal
opinions. It can be used in an e-business context. For example, business managers can analysise
customers' attitudes, as to whether they like or dislike their product or service.
Also, government can use sentiment analysis to analyze citizen perspectives.
In a word, sentiment analysis is coming into widespread use.
As Dr. Haiyun mentions, English language sentiment analysis research has
undergone major developments in recent years \cite{ChineseSentimentAnalysis}.
However, less research has been undertaken in other languages, such as Chinese.
Today, a lot of English language sentiment analysis theories have been
developed. Also, lots of Machine Translation tools are available, such as Google
translation, Bing translation and Yandex translation.
Manchine Translation uses computational linguistic programs and natural language
processing theory \cite{machineTranslation}.
However, nobody working in a combination of these two fields of research has undertaken non-English
sentiment analysis. Therefore, the research described and discussed in this
document aimed to create a testing model to find the best-combination of English
sentiment analysis tools and machine translation tools to obtain reliable
sentiment analysis results from non-English texts, for non-English speakers who
do not have such sentiment analysis tools to analyze their own language.
In the end, everyone to be able to understand different language speakers' attitudes (positive or negative), emotions and opinions.\\
\section{Literature Review}
This research consists of three components.
Firstly, measuring machine translation service quality.
Secondly, testing sentiment analysis service quality.
Thirdly, finding the best compound mode for machine translation service and
sentiment analysis service.
As a result, this section will fouced doing literature review on machine
translation, Testing methodology and sentiment analysis.
\subsection{Testing in Machine translation}
There are two research articles about testing modeling of machine
translation(MT).

\paragraph{Around Trip Translation method}
As Somers argue that they establish an
around trip translation (RTT) method for detect the quality of machine translation \cite{roundTripTranslation}.
For example, testing English to Chinese translation tool.
Firstly, using English to Chinese translation tool translate test data to
Chinese.
Secondly, translation Chinese translated data back to English.
Finally, compare the similarity for two English data set.
They also metion two similarity metrics BLEU and F-score, to judge the
translations. The limitation of RTT modle are it cannot tell which one is good
MT from all bad MT tools as well as cannot find which sentences are easier for
translation and which sentences are harder for translation.

\paragraph{A monte carlo method for machine translation services}
Another article is about using third-party language to test the quality of machine
translation \cite{thirdPartMachineTranslation}.
For example, if testing English to Chinese translation tool.
Firstly, random choice an Intermediate third-party language.
Secondly, translation English test data to the third-party language, after
translation third-party language to Chinese.
These two steps are only finished one path.
Another path is a translation in English directly to Chinese.
In the end, the comparison the two paths of results similarity. In this article, the main
finding is Google Translate is the best machine translation. In addition, there
is a tendency to be produced better results in European languages, which use
ANOVA Statistics method and Pairwise t tests getting this conclusion.
In my experiment, I also got Google Translator is the best machine translation compare with Yandex and Baidu.

@@

\begin{tabular}{rr}
  \hline
  Mean Slope & Median Slope \\
  \hline
  0.008788344 & 0.0116933 \\
  \hline
\end{tabular}
\section{Questionnaire}

\bibliographystyle{IEEEtran}
\bibliography{library}
\end{document}

>>>>

Social Media is becoming more and more widely used. There are lots of text comments
on different discussion topics every day.
It would be impossible to analyses the huge amount of data generated manually.
These topics are discussed by speakers of different languages, from different
cultural backgrounds, further complicating any analysis.
Most people enounter language and cultureal barriers during cross-language
communication.
In this paper, the use of machine translation and sentiment analysis tools to
solve this problem of analysing cross-cultural and cross-language data is
explored and discussed.
Sentiment analysis is a part of text data mining. The aim of sentiment analysis
is to determine the attitude of speakers or writers with respect to particular topics
or the overall contextual polarity or emotional reaction to a text document. It is usually equated with
opinion mining, which involves the use of natural language processing and
machine learning to ascertain the possibility of positive or negative opinions \cite{sentimentAnalysis}.
Sentiment analysis is useful for analyzing a huge amount of data relating to personal
opinions. It can be used in an e-business context. For example, business managers can analysise
customers' attitudes, as to whether they like or dislike their product or service.
Also, government can use sentiment analysis to analyze citizen perspectives.
In a word, sentiment analysis is coming into widespread use.
As Dr. Haiyun mentions, English language sentiment analysis research has
undergone major developments in recent years \cite{ChineseSentimentAnalysis}.
However, less research has been undertaken in other languages, such as Chinese.
Today, a lot of English language sentiment analysis theories have been
developed. Also, a variety of Machine Translation tools is available, such as Google
translation, Bing translation and Yandex translation.
Manchine Translation uses computational linguistic programs and natural language
processing theory \cite{machineTranslation}.
However, nobody working in a combination of these two fields of research has undertaken non-English
sentiment analysis. Therefore, the research described and discussed in this paper aims to create a testing model to find the best-combination of English
sentiment analysis tools and machine translation tools to obtain reliable
sentiment analysis results from non-English texts, for non-English speakers who
do not have such sentiment analysis tools to analyze their own language.
Eventually, everyone will be able to understand different language speakers' attitudes (positive or negative), emotions and opinions.\\
\section{Literature Review}
This research consists of three components; measuring machine translation
service quality; testing sentiment analysis service quality;
finding the best compound mode for machine translation service and
sentiment analysis service.
As a result, this section will focus on a review of literature review about machine
translation, Testing methodology and sentiment analysis.
\subsection{Testing in Machine translation}
There are two research articles about testing modeling of machine
translation(MT).

\paragraph{Round Trip Translation method}
As Somers argues, an Around Trip Translation (RTT) method has been establish to
detect the quality of machine translation \cite{roundTripTranslation}; for example, testing English to Chinese translation tools.
Firstly, an English to Chinese translation tool is use to translate test data to
Chinese. It is then used translate Chinese data back to English.
Finally, compare the similarity for two English data set.
They also mention two metrics of similarity, BLEU and F-score, to judge the
translations. The limitations of RTT model are it cannot distingicush the best
MT tool from a group of poor MT tools as well as it cannot find which sentences are easier for
translation and which sentences are harder for translation.

\paragraph{A Monte Carlo Method for machine translation services}
Another article is about using third-party language to test the quality of machine
translation \cite{thirdPartMachineTranslation}, for example, if testing an English to Chinese translation tool.
Firstly, random choose an Intermediate third-party language.
Secondly, translation English test data to the third-party language, after
translates the third-party language to Chinese.
These two steps constitute one path.
Another path is translation from English directly to Chinese.
In the end, the two path results need to compare similarity. In this article, the main
finding is that Google Translate is the best machine translation. In addition,
the better results to be produced in European languages, use ANOVA Statistics method and Pairwise T tests getting this conclusion.
In my experiment, I also got Google Translator is the best machine translation
compare with Yandex and Baidu. Pairwise T tests also can be useful for find best-combination of English
sentiment analysis tools and machine translation tools to obtain reliable
sentiment analysis results. The highlight of this model is using third-party
language, which can decide preference language of machine translation.

@@

\begin{tabular}{rr}
  \hline
  Mean Slope & Median Slope \\
  \hline
  0.008788344 & 0.0116933 \\
  \hline
\end{tabular}
\section{Questionnaire}
\begin{enumerate}
\item What is your gender? \\
  O Male O Female O perfer Not to say
\item What is your age group? \\
  O <18ys O 18-24ys O 24-30ys O 30-40ys O 40-50ys O >50ys
\item What are your areas of interest? (many answers possible) \\
  O Science and Technology O engineering O entertainment O military O politics O
  law O literature O Other (please specify) .....................
\item How often do you use social media ?\\
  O Hourly O Daily O Weekly O monthly O yearly
\item How long do you use social media each time? \\
  O time >= 1 hour O time 30 minutes O 1 hour O 10 minutes to 30 minutes O less than 10 minutes
\item Which social media platforms do you use regularly ? (many answers possible)\\
  O Facebook O Twitter O YouTube O Instagram O WeChat O LinkedIn O Weibo O I
  don't use social media O Other (please specify)
\item Which language(s) can you understand easily ?\\
  O English O French O Chinese O Spanish O Vietnamese O Arabic O Indian O
  Russian O German O Other (please specify)
\item How interested are you in other culture? \\
  O Extremely interested O Very interested O Somewhat interested O Not so
  interested O Not at all interested
\item How willing are you to understand the contents in an foreign language?\\
  O Very likely O Likely O Neither likely nor unlikely O Unlikely O Very
  unlikely

\item How often do you read others' opinion ?\\
  O Always O Usually O Sometimes O Rarely O Never

\item Which machine translation tool do you use most?\\
  O Google Translation O Microsoft Bing Translation O Yandex Translation O Baidu
  Translation O Youdao Translation O Other (please specify) .......
\item Sentiment analysis tool can determine the attitude (positive or negative)
  of writers, which can be useful for analyzing a huge amount of comments. Are
  you willing to use this tool to analyze your interests in social
  media, such as product comments or restaurant review, etc?\\
  O Very likely O Likely O Neither likely nor unlikely O Unlikely O Very unlikely
\end{enumerate}
\bibliographystyle{IEEEtran}
\bibliography{library}
\end{document}
